% REVIEW: Yaku Contents
\section{Yaku}\label{core:sec:yaku}

\subsection{1 Han Yaku}\label{core:ssec:1-han-yaku}

\yaku{Riichi}{Riichi}{リーチ}
	{\closedhand \\ 
	\upgradesto Enables Ippatsu~\pr{yaku}{Ippatsu} \\ 
	\upgradestoother Enables Ura~Dora~\pr{bonus}{Ura Dora} \\ 
	\upgradesto Upgrades into Double~Riichi~\pr{yaku}{Double Riichi}}
	{Declare Riichi. That is, while you have a ready hand, and it is a closed hand, wager 1,000 points and discard a tile sideways. You can only discard the tile you draw from that point on.}

\yaku{Ippatsu}{One Shot}{\ruby{一発}{いっぱつ}}
	{\closedhand \\ 
	\brokenhand \\
	\upgradesfrom Requires Riichi~\pr{yaku}{Riichi}}
	{Win on or before your next turn after declaring Riichi.}

\yaku{Double Riichi}{Double Riichi}{ダブルリーチ}
	{\closedhand \\ 
	\upgradesto Enables Ippatsu~\pr{yaku}{Ippatsu} \\ 
	\upgradesfrom Stacks with Riichi~\pr{yaku}{Riichi}}
	{Declare Riichi on your first turn.}

\yaku{Menzen Tsumo}{Fully Concealed Tsumo}{\ruby{門前清自摸和}{メンゼンチンツモホー}}
	{\closedhand}
	{While your hand is closed, draw a tile that completes your hand.}

\yaku{Pinfu}{Pinfu}{\ruby{平和}{ピンフ}}
	{\closedhand \\
	\upgradestoother Has specific Fu values~\prs{fu}{Kuipinfu}{Pindzumo}}
	{Your hand does not generate any additional fu. That is, your hand is all sequences, your pair is not a Yakuhai~\pr{yaku}{Yakuhai}, and the final block waiting to be filled is an open ended run.}

\yaku{Iipeikou}{Twin Sequences}{\ruby{一盃口}{イーペーコー}}
	{\closedhand \\
	\upgradesto Upgrades to Ryanpeikou~\pr{yaku}{Ryanpeikou}}
	{Have two copies of the same sequence in your hand. \textit{(Differently colored tiles are counted the same as their basic equivalent.)}}

\yaku{Haitei Raoyue}{Under the Sea}{\ruby{海底撈月}{ハイテイラオユエ}}
	{}
	{Win by drawing the last tile in the live wall.}

\yaku{Houtei Raoyui}{Under the River}{\ruby{河底撈魚}{ホーテイラオユイ}}
	{}
	{While there are no tiles in the live wall, win off a discard.}

\yaku{Rinshan Kaihou}{After a Kan}{\ruby{嶺上開花}{リンシャンカイホウ}}
	{\symbnegate Negates Haitei~Raoyue~\pr{yaku}{Haitei Raoyue}}
	{After calling a Kan, win off the replacement tile drawn from the dead wall.}

\yaku{Chankan}{Robbing a Kan}{\ruby{搶槓}{チャンカン}}
	{}
	{As a player upgrades a Pon to a Kan, win off the tile used to perform the upgrade. The Kan does not resolve and is interrupted. You can claim this off a Closed Kan for Kokushi~Musou~\pr{yaku}{Kokushi Musou}}

\yaku{Yakuhai}{Valued Tile}{\ruby{役牌}{やくはい}}
	{\upgradesto A collective term for Jikaze~\pr{yaku}{Jikaze}, Bakaze~\pr{yaku}{Bakaze}, Sangenpai~\pr{yaku}{Sangenpai}}
	{This is a name for a group of Yaku. Each of them ask for a group of a type of Honour tile.}

\yaku{Jikaze}{Seat Wind}{\ruby{自風}{じかぜ}}
	{\upgradesfrom A type of Yakuhai~\pr{yaku}{Yakuhai}\\
	\upgradesto Upgrades into Renfuu~\pr{yaku}{Renfuu} with Jikaze~\pr{yaku}{Jikaze}\\
	\upgradesto Upgrades into Shousuushii~\pr{yaku}{Shousuushii}}
	{Have a group of the wind corresponding to your seat.}

\yaku{Bakaze}{Round Wind}{\ruby{場風}{ばかぜ}}
	{\upgradesfrom A type of Yakuhai~\pr{yaku}{Yakuhai}\\
	\upgradesto Upgrades into Renfuu~\pr{yaku}{Renfuu} with Bakaze~\pr{yaku}{Bakaze}\\
	\upgradesto Upgrades into Shousuushii~\pr{yaku}{Shousuushii}}
	{Have a group of the wind corresponding to the current round.}

\yaku{Sangenpai}{Dragon Tiles}{\ruby{三元牌}{さんげんパイ}}
	{\upgradesfrom A type of Yakuhai~\pr{yaku}{Yakuhai}\\
	\upgradesto Upgrades into Shousangen~\pr{yaku}{Shousangen}}
	{Have a group of any dragon tile.}

\yaku{Tanyao}{All Simples}{\ruby{断幺九}{タンヤオチュー}}
	{}
	{None of the tiles in your hand are Orphan tiles.}

\yaku{Sanshoku Doujun}{Mixed Triple Sequences}{\ruby{三色同順}{さんしょくどうじゅん}}
	{\morevaluable More Valuable if Closed~\pr{yaku}{Menzen Sanshoku Doujun}}
	{Have the same numbered run in each of the three numbered suits.}

\yaku{Ittsuu}{Full Straight}{\ruby{一気通貫}{いっきつうかん}}
	{\morevaluable More Valuable if Closed~\pr{yaku}{Menzen Ittsuu}}
	{Have a seuqence of 123, 456, 789 in the same suit as one another.}

\yaku{Chanta}{Half Outside Hand}{\ruby{混全帯公九}{ホンチャンタイヤオチュウ}}
	{\morevaluable More Valuable if Closed~\pr{yaku}{Menzen Chanta}\\
	\upgradesto Upgrades into Junchan~\prs{yaku}{Junchan}{Menzen Junchan}\\
	\upgradesto Upgrades into Honroutou~\pr{yaku}{Honroutou}}
	{Each block in your hand contains at least one Orphan tile.}


\subsection{2 Han Yaku}\label{core:ssec:2-han-yaku}

\yaku{Chiitoitsu}{Seven Pairs}{\ruby{七対子}{チートイツ}}
	{\closedhand \\
	\upgradestoother Has specific Fu value~\pr{fu}{Chiitoitsu}.}
	{Your hand is made up of seven pairs.}

\yaku{Renfuu}{Double Wind}{\ruby{連風}{れんプー}}
	{\upgradesfrom Upgrades from Jikaze~\pr{yaku}{Jikaze} and Bakaze~\pr{yaku}{Bakaze}\\
	\upgradesto Upgrades to Shousuushii~\pr{yaku}{Shousuushii}}
	{Have a group of Wind tiles that is both your seat wind and the round wind.}

\yaku{Shousangen}{Small Three Dragons}{\ruby{小三元}{しょうさんげん}}
	{\upgradesfrom Upgrades from Two Copies of Sangenpai~\pr{yaku}{Sangenpai}\\ 
	\upgradesto Upgrades to Daisangen~\pr{yaku}{Daisangen}}
	{Have two groups of Dragon tiles, with your pair being the third Dragon tile.}

\yaku{Menzen Sanshoku Doujun}{Closed Mixed Triple Sequences}{\ruby{門前}{メンゼン}\ruby{三色同順}{さんしょくどうじゅん}}
	{\closedhand \\ 
	\lessvaluable Less valuable when Opened~\pr{yaku}{Sanshoku Doujun}}
	{With a closed hand, have the same run in each of the three numbered suits.}

\yaku{Menzen Ittsuu}{Closed Full Straight}{\ruby{門前}{メンゼン}\ruby{一気通貫}{いっきつうかん}}
	{\closedhand \\
	\lessvaluable Less valuable when Opened~\pr{yaku}{Ittsuu}}
	{With a closed hand, have a seuqence of 123, 456, 789 in the same suit as one another.}

\yaku{Menzen Chanta}{Closed Half Outside Hand}{\ruby{門前}{メンゼン}\ruby{混全帯公九}{ホンチャンタイヤオチュウ}}
	{\closedhand \\ 
	\lessvaluable Less valuable when Opened~\pr{yaku}{Chanta} \\
	\upgradesto Upgrades to Junchan~\prs{yaku}{Junchan}{Menzen Junchan}}
	{With a closed hand, have each block in your hand contain at least one Orphan tile.}

\yaku{Junchan}{Full Outside Hand}{\ruby{純全帯公九}{ジュンチャンタイヤオチュウ}}
	{\morevaluable More valuable if Closed~\pr{yaku}{Menzen Junchan} \\ 
	\upgradesfrom Upgrades from Chanta~\prs{yaku}{Chanta}{Menzen Chanta} \\
	\upgradesto Upgrades into Chinroutou~\pr{yaku}{Chinroutou}}
	{Each block in your hand must contain at least one Terminal tile.}

\yaku{Honroutou}{All Terminals and Honours}{\ruby{混老頭}{ホンロウトウ}}
	{\upgradesfrom Upgrades from Chanta~\prs{yaku}{Chanta}{Menzen Chanta} \\
	\upgradesto Upgrades into Chinroutou~\pr{yaku}{Chinroutou}}
	{Each block in your hand must be comprised of only Orphan tiles.}

\yaku{Toitoi}{All Triplets}{\ruby{対々和}{トイトイホー}}
	{\upgradesto Upgrades to Suuankou~\pr{yaku}{Suuankou}\\
	\upgradesto Upgrades to Suukantsu~\pr{yaku}{Suukantsu}}
	{All blocks in your hand must be groups.}

\yaku{Sanankou}{Three Concealed Triplets}{\ruby{三暗刻}{サンアンコー}}
	{\upgradesto Upgrades to Suuankou~\pr{yaku}{Suuankou}}
	{Your hand contains three closed groups.}

\yaku{Sankantsu}{Three Kans}{\ruby{三槓子}{サンカンツ}}
	{\upgradesto Upgrades to Suukantsu~\pr{yaku}{Suukantsu}}
	{Your hand contains three Kans.}

\yaku{Sanshoku Doukou}{Triple Triplets}{\ruby{三色同刻}{さんしょくどうコー}}
	{}
	{Have the same numbered group in each of the three numbered suits.}

\yaku{Honitsu}{Half Flush}{\ruby{混一色}{ホンイーツー}}
	{\upgradesto Upgrades to Chinitsu~\prs{yaku}{Chinitsu}{Menzen Chinitsu}}
	{Your hand contains tiles from only one numbered suit and Honour tiles.}


\subsection{3 Han Yaku}\label{core:ssec:3-han-yaku}

\yaku{Ryanpeikou}{Double Twin Sequences}{\ruby{二盃口}{リャンペーコー}}
	{\closedhand \\ 
	\upgradesfrom Upgrades from Iipeikou~\pr{yaku}{Iipeikou}}
	{Have two copies each of two sequences in your hand. \textit{(Differently colored tiles are counted the same as their basic equivalent)}}

\yaku{Menzen Junchan}{Closed Fully Outside Hand}{\ruby{門前}{メンゼン}\ruby{純全帯公九}{ジュンチャンタイヤオチュウ}}
	{\closedhand \\ 
	\lessvaluable Less valuable when Opened~\pr{yaku}{Junchan}\\
	\upgradesfrom Upgrades from Chanta~\prs{yaku}{Chanta}{Menzen Chanta} \\
	\upgradesto Upgrades into Chinroutou~\pr{yaku}{Chinroutou}}
	{With a closed hand, each block in your hand must contain at least one Terminal tile.}

\yaku{Menzen Honitsu}{Closed Half Flush}{\ruby{門前}{メンゼン}\ruby{混一色}{ホンイーツー}}
	{\closedhand \\
	\morevaluable Less valuable if Opened~\pr{yaku}{Honitsu}\\
	\upgradesto Upgrades to Chinitsu~\prs{yaku}{Chinitsu}{Menzen Chinitsu}}
	{With a closed hand, it is made of tiles from only one numbered suit and Honour tiles.}


\subsection{5 Han Yaku}\label{core:ssec:5-han-yaku}

\yaku{Chinitsu}{Full Flush}{\ruby{清一色}{チンイーツー}}
	{\morevaluable More valuable when Closed~\pr{yaku}{Menzen Chinitsu} \\
	\upgradesfrom Upgrades from Honitsu~\prs{yaku}{Honitsu}{Menzen Honitsu}}
	{Your hand contains tiles from only one numbered suit.}


\subsection{6 Han Yaku}\label{core:ssec:6-han-yaku}

\yaku{Menzen Chinitsu}{Closed Full Flush}{\ruby{門前}{メンゼン}\ruby{清一色}{チンイーツー}}
	{\closedhand \\
	\lessvaluable Less valuable when Opened~\pr{yaku}{Chinitsu} \\
	\upgradesfrom Upgrades from Honitsu~\prs{yaku}{Honitsu}{Menzen Honitsu}}
	{With a closed hand, it is made of tiles from only one numbered suit.}

\subsection{Yakuman}\label{core:ssec:yakuman-yaku}

\yaku{Tenhou}{Blessing of Heaven}{\ruby{天和}{テンホー}}
	{\closedhand}
	{While you are the dealer, win on your opening hand.}

\yaku{Chiihou}{Blessing of Earth}{\ruby{地和}{チーホー}}
	{\closedhand \\
	\brokenhand}
	{While you are not the dealer, win on your first draw.}

\yaku{Daisangen}{Big Three Dragons}{\ruby{大三元}{だいさんげん}}
	{\upgradesfrom Upgrades from Shousangen~\pr{yaku}{Shousangen}}
	{Your hand contains three groups of Dragon tiles.}

\yaku{Shousuushii}{Small Four Winds}{\ruby{小四喜}{ショースーシー}}
	{\upgradesfrom Upgrades from Jikaze~\pr{yaku}{Jikaze}\\
	\upgradesfrom Uprgades from Bakaze~\pr{yaku}{Bakaze}\\
	\upgradesfrom Upgrades from Renfuu~\pr{yaku}{Renfuu} \\
	\upgradesto Upgrades into Daisuushii~\pr{yaku}{Daisuushii}}
	{Your hand contains three groups of Wind tiles, with your pair being the fourth.}

\yaku{Chinroutou}{All Terminals}{\ruby{清老頭}{チンロウトウ}}
	{\upgradesfrom Upgrades from Junchan~\prs{yaku}{Junchan}{Menzen Junchan} \\
	\upgradesfrom Upgrades from Honroutou~\pr{yaku}{Honroutou}}
	{Your hand contains only Terminal tiles.}

\yaku{Tsuuiisou}{All Honours}{\ruby{字一色}{ツーイーソー}}
	{}
	{Your hand contains only Honour tiles.}

% REVIEW: Is Suuankou a closed hand?
\yaku{Suuankou}{Four Concealed Triplets}{\ruby{四暗刻}{スーアンコー}}
	{\upgradesfrom Upgraded from Toitoi~\pr{yaku}{Toitoi} \\
	\upgradesfrom Upgraded from Sanankou~\pr{yaku}{Sanankou} \\
	\upgradesto Upgrades to Suuankou~Tanki~\pr{yaku}{Suuankou Tanki}}
	{Your hand contains four closed groups.}

\yaku{Suukantsu}{Four Kans}{\ruby{四槓子}{スーカンツ}}
	{\upgradesfrom Upgraded from Toitoi~\pr{yaku}{Toitoi} \\
	\upgradesfrom Upgraded from Sankantsu~\pr{yaku}{Sankantsu}}
	{Your hand contains four Kans.}

\yaku{Ryuuiisou}{All Green}{\ruby{緑一色}{リューイーソー}}
	{}
	{Your hand only contains tiles which are entirely green. You don't need to use the green dragon. Those tiles are: {\mahjong{23468s6z}}.}

\yaku{Chuurenpoutou}{Nine Gates}{\ruby{九連宝灯}{チュウレンポウトウ}}
	{\closedhand \\
	\upgradesto Upgrades to Junsei~Chuurenpoutou~\pr{yaku}{Junsei Chuurenpoutou}}
	{Your hand contains the following pattern in only one numbered suit: 1112345678999, with an additional tile in the same numbered suit.}

\yaku{Kokushi Musou}{Thirteen Orphans}{\ruby{国士無双}{こくしむそう}}
	{\closedhand \\
	\upgradesto Upgrades to Kokushi~Musou~Juusanmen~Machi~\pr{yaku}{Kokushi Musou Juusanmen Machi}}
	{Your hand contains the following pattern: {\mahjong{19m19p19s1234567z}}, with an additional Orphan tile.}


\subsection{Double Yakuman}\label{core:ssec:double-yakuman-yaku}

\yaku{Daisuushii}{Big Four Winds}{\ruby{大四喜}{ダイスーシー}}
	{\upgradesfrom Upgrades from Shousuushii~\pr{yaku}{Shousuushii}}
	{Your hand contains four groups of Wind tiles.}

\yaku{Suuankou Tanki}{Four Concealed Triplets, Single Tile Wait}{\ruby{四暗刻}{スーアンコー}\ruby{単騎待ち}{たんきまち}}
	{\upgradesfrom Upgrades from Suuankou~\pr{yaku}{Suuankou}}
	{Your hand contains four closed groups.}

\yaku{Junsei Chuurenpoutou}{Pure Nine Gates}{\ruby{純正}{じゅんせい}\ruby{九連宝灯}{チュウレンポウトウ}}
	{\closedhand \\
	\upgradesfrom Upgrades from Chuurenpoutou~\pr{yaku}{Chuurenpoutou}}
	{The closed part of your hand contains the following pattern in only one numbered suit: 1112345678999, with an additional tile in the same numbered suit.}

\yaku{Kokushi Musou Juusanmen Machi}{Thirteen Orphans Thirteen-sided Wait}{\ruby{国士無双}{こくしむそう}\ruby{十三面待ち}{じゅうさんめんまち}}
	{\closedhand \\
	\upgradesfrom Upgrades from Kokushi~Musou~\pr{yaku}{Kokushi Musou}}
	{Your hand without your winning tile contains the following pattern: {\mahjong{19m19p19s1234567z}}.}